### 2020-06-15 analysis_and_paper/supplements.Rmd
Corrects some paths and knitts analysis for experiment 1 and supplements.
Updated via the Open Science Framework

author: 
  - name          : Tobias Heycke
    affiliation   : 1, 2
    corresponding : yes    
    address       : "P.O. 122155, 68072 Mannheim, Germany"
    email         : "tobias.heycke@gesis.org"
  - name        : Frederik Aust
    affiliation : 1
  - name        : Mahzarin R. Banaji
    affiliation : 3
  - name        : John G. Conway
    affiliation : 4
  - name        : Pieter Van Dessel
    affiliation : 5
  - name        : Xiaoqing Hu
    affiliation : 6    
  - name        : Congjiao Jiang
    affiliation : 4    
  - name        : Benedek Kurdi
    affiliation : 3    
  - name        : Robert Rydell
    affiliation : 7
  - name        : Lisa Spitzer
    affiliation : 1
  - name        : Christoph Stahl
    affiliation : 1
  - name        : Christine A. Vitiello
    affiliation : 4
  - name        : Jan De Houwer
    affiliation : 5

affiliation:
  - id          : 1
    institution : University of Cologne
  - id          : 2
    institution : GESIS - Leibniz Institute for the Social Sciences
  - id          : 3
    institution : Harvard University 
  - id          : 4
    institution : University of Florida 
  - id          : 5
    institution : Ghent University 
  - id          : 6
    institution : The University of Hong Kong 
  - id          : 7
    institution : Indiana University

bibliography      : ["references.bib", "r-references.bib"]
#appendix          : "appendix.Rmd"

@@

source("https://gist.githubusercontent.com/crsh/be88be19233f1df4542aca900501f0fb/raw/f258053d144681bd4a5b86ed0956da7dc3f380ee/gglegend.R")
```

```{r analysis-preferences}
# Data location
raw_data_path <- "../ml-otm1/results/data_raw/"
processed_data_path <- "../ml-otm1/results/data_processed/"

@@

## Ugly hack to overcome bug in ggplot2, https://github.com/tidyverse/ggplot2/issues/2058
# assignInNamespace("theme_nothing", function() {
#     theme_void() + theme(axis.text.x = NULL, axis.text.y = NULL, axis.line.x = element_blank(), axis.line.y = element_blank())
# }, "cowplot")

@@

In the following we report additional analyses and provide details for the model specification used for the Bayesian model comparisons.
We report results from the linear mixed model analysis of the IAT response times, from prior sensitivity analyses for the Bayesian model comparisons, and from an exploratory analysis of the relationship between US recognition accuracy and associative learning.
Table\ \@ref(tab:otm1-participant-table) summarizes the participants' demographics separately for each location of data collection.

@@

@@

We analyzed standardized response latencies, that is, the time that elapsed between stimulus presentation and *correct* response divided by the standard deviation of all response latencies in a given block, Figure\ \@ref(fig:otm1-iat-plot).
To assess the reversal of the response mapping effect, we contrasted the common response mapping of Bob and negative words with the common mapping of Bob and positive words.
Hence, larger values represent more favorable implicit evaluations.

@@

```{r otm1-iat-plot, fig.cap = "(ref:otm1-iat-plot)"}
otm1_results_legend <- guide_legend(
    # title = "Valence order\nDescriptions of Bob\n(Briefly presented primes)"
    title = expression(atop("Valence order", atop(scriptstyle("Learned behaviors"), scriptstyle("(Briefly presented USs)"))))
    , title.position = "top"
    , title.hjust = 0.5
    , reverse = TRUE
    , keyheight = 2
  )

@@

@@

<!-- (ref:otm1-iat-lmer-contrasts) Planned contrasts of changes in congruency effects across learning blocks for the linear mixed model analysis of standardized IAT response times. -->

```{r otm1-lmer-emm-2, cache = TRUE, results = "asis"}
otm1_iat_lmer_contrasts <- contrast(
  otm1_iat_lmer_emm
  , list(
    "Negative-positive" = c(1, -1, -1, 1, 0, 0, 0, 0)
    , "Positive-negative" = c(0, 0, 0, 0, 1, -1, -1, 1)
  )
) %>%
  apa_print

# otm1_iat_lmer_contrasts %$%
#   table %>%
#   rename("Valence order" = contrast) %>%
#   apa_table(
#     caption = "(ref:otm1-iat-lmer-contrasts)"
#     , escape = FALSE
#     , row.names = FALSE
#   )
```

In line with the conventional ANOVA analysis, we found that response time differences suggested more favorable evaluations of Bob after the first than after the second block when the learned behaviors were first positive and later negative, `r otm1_iat_lmer_contrasts$full_result$Positive_negative`.
Vice versa, response time differences suggested more favorable evaluations after the second than after the first block when descriptions of Bob were first negative and later positive, `r otm1_iat_lmer_contrasts$full_result$Negative_positive`.
Again, these results indicate that the explicit evaluations and IAT scores were consistent.

@@

# Bayesian model comparison

@@

#### Explicit and implicit measures

@@

```{r load-data-and-design-matrices}
tmp <- lazyLoad(tools::file_path_sans_ext(list.files(pattern = "otm1-bayesian-replication-restructure_", recursive = TRUE)[1]))
tmp <- lazyLoad(tools::file_path_sans_ext(list.files(pattern = "otm1-bayesian-replication-design-matrix_", recursive = TRUE)[1]))

otm1_n <- as.integer(nlevels(otm1_attitudes_collapsed$ParticipantNumber))
```

```{r otm1-prior-sensitivity-replication, cache = TRUE, warning=FALSE}
replication_rscales <- expand.grid(
  iat = seq(0.5, 1, length.out = 3)
  , rating = seq(sqrt(2)/2, 2, length.out = 3)
) %>% 
  filter(iat <= rating) %>%
  as.matrix %>% 
  `/`(., sqrt(2)) %>% # Rescale to ANOVA specification (see https://forum.cogsci.nl/discussion/3746/bayesfactor-scale-of-cauchy-prior-in-t-tests-and-anova)
  as.data.frame

@@

## Prime recogniton and implicit evaluations

@@

```{r otm1-rydell-recognition-plot, fig.cap = "(ref:otm1-rydell-recognition-plot)", fig.width = 3.5, fig.height = 2.5}
otm1_mem %>%
  ggplot(aes(x = Location, y = Accuracy, shape = Location, fill = Location)) +
  geom_hline(yintercept = 0.5, color = grey(0.5)) +
  geom_violin(alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(alpha = 0.5, size = 1) +
  # stat_summary(fun.y = mean, aes(group = Location, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, color = "black", fun.args = list(B = 10000)) +
  # scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
  # scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_shape_manual(values = c(21, 23, 24)) +
  scale_color_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  scale_fill_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  labs(
    x = "Location"
    , y = "US recognition accuracy"
  ) +
  theme(legend.position = "none")
```

In contrast to the original results reported by @rydell_two_2006, US recognition accuracy in this study was above chance, Figure\ \@ref(fig:otm1-rydell-recognition-plot).
Memory for USs may, thus, have interfered with the associative learning process and prevented the predicted reversal of the IAT score differences.
We, therefore, performed an exploratory regression analysis of US recognition and the IAT score difference between blocks used in the Bayesian analysis above.
Positive values represent a more favorable evaluation after the block in which Bob was paired with positive learned behaviors and briefly presented negative USs.
Conversely, negative IAT score difference between blocks indicate that the IAT effects reflect the valence of the briefly presented USs.
If US recognition indeed obstructed the associative learning process, we would expect to observe a positive relationship between US recognition accuracy and IAT score differences between blocks:
When US recognition is high, IAT score differences should reflect the valence of the learned behaviors but not with the US valence.
We would expect to observe smaller and eventually negative IAT score differences as US recognition accuracy declines and associative learning takes over.

(ref:prime-recognition-iat-difference) Scatterplot of prime recognition accuracy and evaluative differences in IAT scores between blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.

@@

otm1_iat_delta %>%
  ggplot(aes(x = Accuracy, y = delta)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "black") +
  labs(
    x = "US recognition accuracy"
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  theme_apa()
```

```{r prime-recognition-iat-difference-regression, results = "asis"}
otm1_recognition_iat_lm_bf <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  as.data.frame %>%
  lmBF(delta ~ Accuracy, data = .) %>%
  apa_print

otm1_iat_delta_lm_res <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  lm(delta ~ Accuracy, data = .) %>% 
  apa_print
```

However, we were unable to detect any relationship between US recognition accuracy and IAT score differences between blocks, `r otm1_iat_delta_lm_res$full_result$Accuracy`; the data even provide some evidence against such a relationship, `r otm1_recognition_iat_lm_bf$statistic`.
We centered US recognition at .5 and found that the intercept of the regression line was greater than zero, which indicates a positive IAT score difference despite at-chance US recognition accuracy, `r otm1_iat_delta_lm_res$full_result$Intercept`.
Hence, even for participants who exhibited no memory for briefly presented USs, IAT score differences reflected the valence of the learned behaviors, see Figure\ \@ref(fig:prime-recognition-iat-difference).
These results provide no indication that the deviation of our findings from those reported by @rydell_two_2006 are attributable to the above-chance US recognition accuracy in this study.

<!--
#### Prime valence memory

TODO TH: Is this supposed to be in the paper? 
TH: No - maybe not even online supplement?

```{r listPrimes, echo = FALSE, eval=FALSE}

# correct names of primes
eng_pos <- c("Flower",
            "Friend",
            "Gift",
            "Happy",
            "Puppy",
            "Pretty",
            "Party",
            "Kiss",
            "Kitten",
            "Smile")

eng_neg <- c("Corpse",
            "Death",
            "Hell",
            "Pain",
            "War",
            "Hurt",
            "Spider",
            "Stink",
            "Trash",
            "Ugly")

nl_pos <- c("Bloem",
            "Vriend",
            "Geschenk",
            "Blij",
            "Puppy",
            "Mooi",
            "Feest",
            "Kus",
            "Katje",
            "Glimlach")

nl_neg <- c("Lijk",
            "Dood",
            "Hel",
            "Pijn",
            "Oorlog",
            "Letsel",
            "Spin",
            "Stank",
            "Afval",
            "Lelijk")

ger_pos <- c("Blume",
            "Freund",
            "Geschenk",
            "Glücklich",
            "Welpe",
            "Hübsch",
            "Party",
            "Kuss",
            "Kätzchen",
            "Lächeln")

ger_neg <- c("Leiche",
            "Tod",
            "Hölle",
            "Schmerz",
            "Krieg",
            "Verletzung",
            "Spinne",
            "Gestank",
            "Abfall",
            "Hässlich")

# prep data frame to correspond with correct names

otm1_mem$chosenItems <- gsub("\\r", "", otm1_mem$chosenItems, fixed = TRUE)
otm1_mem$chosenItems <- gsub("u'", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("'", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("\\", "", otm1_mem$chosenItems, fixed = TRUE)
otm1_mem$chosenItems <- gsub("ï»¿", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("[", "", otm1_mem$chosenItems, fixed = TRUE) 
otm1_mem$chosenItems <- gsub("]", "", otm1_mem$chosenItems, fixed = TRUE)

otm1_mem$chosenItems <- gsub("xfc", "ü", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xe4", "ä", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xf6", "ö", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xdf", "ß", otm1_mem$chosenItems)

otm1_mem <- separate(otm1_mem, 
                     col = "chosenItems", 
                     into = paste0("chosen", 1:20), 
                     sep = ", ")

pos <- c(eng_pos, nl_pos, ger_pos)
neg <- c(eng_neg, nl_neg, ger_neg)
otm1_mem$poscor <- 0
otm1_mem$negcor <- 0

>>>>

author: 
  - name          : Tobias Heycke
    affiliation   : "1,2"
    corresponding : yes    
    address       : "P.O. 122155, 68072 Mannheim, Germany"
    email         : "tobias.heycke@gesis.org"
  - name          : Frederik Aust
    affiliation   : "1"
  - name          : Mahzarin R. Banaji
    affiliation   : 3
  - name          : Jeremy Cone
    affiliation   : 9
  - name          : Pieter Van Dessel
    affiliation   : 5
  - name          : Melissa J. Ferguson
    affiliation   : 8
  - name          : Xiaoqing Hu
    affiliation   : 6    
  - name          : Congjiao Jiang
    affiliation   : 4    
  - name          : Benedek Kurdi
    affiliation   : "3,8"
  - name          : Robert Rydell
    affiliation   : 7
  - name          : Lisa Spitzer
    affiliation   : 1
  - name          : Christoph Stahl
    affiliation   : 1
  - name          : Christine Vitiello
    affiliation   : 4
  - name          : Jan De Houwer
    affiliation   : 5

affiliation:
  - id            : 1
    institution   : University of Cologne
  - id            : 2
    institution   : GESIS - Leibniz Institute for the Social Sciences
  - id            : 3
    institution   : Harvard University 
  - id            : 4
    institution   : University of Florida 
  - id            : 5
    institution   : Ghent University 
  - id            : 6
    institution   : The University of Hong Kong 
  - id            : 7
    institution   : Indiana University
  - id            : 8
    institution   : Cornell University
  - id            : 9
    institution   : Williams College

bibliography      : ["references.bib", "r-references.bib"]

@@

# devtools::install_github("arcaldwell49/Superpower")
library("Superpower")

source("https://gist.githubusercontent.com/crsh/be88be19233f1df4542aca900501f0fb/raw/f258053d144681bd4a5b86ed0956da7dc3f380ee/gglegend.R")
source("error_in_variables.R")
source("effect_sizes.R")
```

```{r analysis-preferences}
# Data location
raw_data_path <- "../otm1/results/data_raw/"
processed_data_path <- "../otm1/results/data_processed/"

@@

@@

In the following we report details on our power analysis, the model specification used for the Bayesian model comparisons, and additional secondary analyses.
We report results from the linear mixed model analysis of the IAT response times, from prior sensitivity analyses for the Bayesian model comparisons, and from an exploratory analysis of the relationship between the recognition accuracy of briefly flashed words and associative learning.
Table\ \@ref(tab:otm1-participant-table) summarizes the participants' demographics separately for each location of data collection.

@@

## Power analysis

The prediction, which is supported by all previous empirical reports, is a crossed disordinal interaction between the factor *learning block* and the control factor *valence order*.
Therefore, our power analyses focuses on this interaction and the theoretically relevant simple effects of *learning block*.
We estimate the sensitivity of our design using the R-package *Superpower* [@R-Superpower] for the contrast analyes using the R-package *emmeans* [@R-emmeans].

```{r rydell-effects, cache = TRUE}
rydell_pes <- 0.1
rydell_f <- 4.78
rydell_n <- 50
rydell_dz <- pes_to_dz(rydell_pes, rydell_n, n_groups = 2)

heycke_t <- c(2.54, 1.45)
heycke_n <- c(28, 26)
heycke_dz <- heycke_t / sqrt(heycke_n)
heycke_pes <- dz_to_pes(heycke_dz, heycke_n, n_groups = 1)
```

```{r otm1-power, cache = TRUE}
otm1_power <- function(f, rm_cor, n = 76, alpha = 0.05) {
  contrast_code <- tibble::tibble(
    a = rep(contr.sum(2), 2)
    , b = rep(contr.sum(2), each = 2)
    , x = a*b * -1
  )

  mu <- with(
    contrast_code
    , f * x +
      - 0.25 * a
  )

  cor_mat <- diag(4)
  triangular <- c(0, 1, 0, 0, 1, 0)
  cor_mat[upper.tri(cor_mat)] <- triangular * rm_cor
  cor_mat[lower.tri(cor_mat)] <- triangular * rm_cor

  string <- "2w*2b"
  labelnames <- c("block", "1", "2", "order", "n-p", "p-n")

  design_result <- ANOVA_design(
    design = string
    , n = n
    , mu = mu
    , sd = 1
    , r = cor_mat
    , labelnames = labelnames
  )

  otm1_power <- ANOVA_exact(
    design_result
    , alpha_level = alpha
    , emm = TRUE
    , verbose = FALSE
    , contrast_type = "pairwise"
    , emm_comp = "block | order"
  )

  otm1_power
}

otm1_n <- 76

# 95% power
otm1_pes <- 0.08068
otm1_dz <- pes_to_dz(otm1_pes, otm1_n, n_groups = 2)
# rho <- 0.5
# f <- dz_to_f(otm1_dz, rho)
# 
# otm1_contrast_power <- otm1_power(f = f, n = otm1_n, rm_cor = rho)$emmeans$contrasts %>%
#   emmeans_power(alpha = 0.05) %>%
#   .[1, ]
# otm1_contrast_power

# 80% power
otm1_pes2 <- 0.050336
otm1_dz2 <- pes_to_dz(otm1_pes2, otm1_n, n_groups = 2)
# f <- dz_to_f(otm1_dz2, rho)
# 
# otm1_contrast_power2 <- otm1_power(f = f, n = otm1_n, rm_cor = rho)$emmeans$contrasts %>%
#   emmeans_power(alpha = 0.05) %>%
#   .[1, ]
# otm1_contrast_power2
```

@rydell_two_2006 found the smallest learning block difference for IAT scores, $\hat\eta_p^2 = `r printp(rydell_pes)`$, $d_z \approx `r rydell_dz`$.
The learning block differences reported by @heycke_two_2018 were of similar magnitude but with an opposite sign.
Across all labs ($N = 152$), our design has 95% power to detect effects as small as $\eta^2_p = `r printp(otm1_pes)`$ ($\delta_z = `r otm1_dz`$) and 80% power to detect effects as small as $\eta^2_p = `r printp(otm1_pes2)`$ ($\delta_z = `r otm1_dz2`$) in two-sided tests.
Thus, our design is sufficiently sensitive to detect (or rule out) differences `r round((1 - otm1_dz/rydell_dz) * 100)`% smaller than the smallest learning block difference reported by @rydell_two_2006.
Figure\ \@ref(fig:otm1-power-curve) illustrates the implied sensitivity in units of Cohen's $\delta$ depending on the assumed repeated-measures correlation $\rho$.

(ref:otm1-power-curve) Sensitivity curves for learning block contrasts in Experiment 1 depending on the assumed repeated measures correlation.
The grey dashed line at the top represents the smallest estimate of the learning block difference reported by Rydell et al. [$d_z = `r rydell_dz`$; -@rydell_two_2006].

```{r otm1-power-curve, fig.width = 5.75, fig.height = 4, fig.cap = "(ref:otm1-power-curve)"}
rydell_power_curve <- tibble(
  rho = seq(-1, 1, length.out = 100)
  , delta = c(
    dz_to_f(rydell_dz, unique(rho)) * 2
  )
  , power = NA
)

otm1_power_curve <- tibble(
  rho = rep(seq(-1, 1, length.out = 100), 2)
  , delta = c(
    dz_to_f(otm1_dz, unique(rho)) * 2
    , dz_to_f(otm1_dz2, unique(rho)) * 2
  )
  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
)

otm1_power_curve %>% 
  mutate(
    power = relevel(factor(power), "0.95")
  ) %>% 
  ggplot(aes(x = rho, y = delta, group = power, linetype = power)) +
  geom_line(data = rydell_power_curve, aes(group = power), color = grey(0.8), linetype = "dashed") +
  geom_line() +
  ylim(c(0, 1)) +
  scale_linetype_discrete(
    labels = c(
      bquote(.(unique(otm1_power_curve$power)[1])~~(delta[z] == .(printnum(otm1_dz))))
      , bquote(.(unique(otm1_power_curve$power)[2])~~(delta[z] == .(printnum(otm1_dz2))))
    )
  ) +
  labs(
    x = bquote("Correlation between learning blocks ["*rho*"]")
    , y = bquote("Learning block difference [Cohen's"~delta*"]")
    , color = "Contrast"
    , linetype = bquote("Power"~"["*1 - beta*"]")
  ) +
  ggtitle("", subtitle = bquote(list(alpha ==~".05", italic(N) == .(otm1_n*2)))) +
  theme_apa(box = TRUE) + 
  theme(
    panel.grid.major.x = element_line()
    , panel.grid.major.y = element_line()
    , panel.grid.minor.x = element_line()
    , panel.grid.minor.y = element_line()
    , legend.justification = "top"
  )
```

```{r otm1-power-curves, eval = FALSE}
otm1_power_curve <- expand.grid(
  n = 76
  , rho = seq(-0.9, 0.9, length.out = 10)
  , alpha = 0.05
  , d = seq(0, 0.9, length.out = 96)
) %>%
  as_tibble %>% 
  mutate(
    f = d/2
    , generalized_eta_squared = f^2 / (1 + f^2)
    , interaction = NULL
    , contrast = NULL
  )

otm1_power_curve[, c("interaction", "contrast")] <- t(apply(
  otm1_power_curve
  , 1
  , function(x) {
    power <- otm1_power(n = x["n"], f = x["f"], rm_cor = x["rho"], alpha = x["alpha"])

    c(
      power_int = power$main_result["order:block", "power"] / 100
      , power_contrast = emmeans_power(power$emmeans$contrasts, alpha_level = x["alpha"])[1, "power"] / 100
    )
  }
))
```

```{r otm1-power-curves-plot, fig.width = 7, fig.height = 4.5, eval = FALSE}
otm1_annotations <- data.frame(
  label = c(
    paste0("list(italic(N) ==", unique(otm1_power_curve$n)*2, ", alpha == 0.05, epsilon == 1)")
    , paste0("list(italic(n) ==", unique(otm1_power_curve$n), ", alpha == 0.05)")
  )
  , test = factor(
      c("interaction", "contrast")
      , levels = c("interaction", "contrast")
      , labels = c("italic('Learning block')%*%italic('Valence order')", "atop(italic('Learning block')*'-contrasts', 'by'~italic('Valence order'))")
    )
  )

pivot_longer(
  otm1_power_curve
  , cols = c("interaction", "contrast")
  , names_to = "test"
  , values_to = "power"
) %>% 
  mutate(
    test = factor(
      test
      , levels = c("interaction", "contrast")
      , labels = c("italic('Learning block')%*%italic('Valence order')", "atop(italic('Learning block')*'-contrasts', 'by'~italic('Valence order'))")
    )
  ) %>% 
  filter(power <= 0.99) %>% 
  ggplot(aes(x = d, y = power, color = rho, group = rho)) +
    geom_hline(yintercept = c(0.8, 0.95), linetype = "solid", color = grey(0.75), size = 0.25) +
    geom_line(linetype = "solid") +
    geom_text(data = otm1_annotations, aes(x = 0.87, y = 0.09, label = label), inherit.aes = FALSE, parse = TRUE, hjust = 0, vjust = 1) +
    scale_x_continuous(
      name = bquote("Cohen's"~delta)
      , position = "top"
      , breaks = function(x) seq(0, x[2], 0.1)
      , sec.axis = sec_axis(trans = ~ .^2 / (4 + .^2), name = bquote(eta[G]^2), breaks = function(x) { b <- seq(0, (2*sqrt(x[2]))/sqrt(1 - x[2]), 0.1); b^2 / (4 + b^2) }, labels = printp)
    ) +
    scale_y_continuous(
      name = bquote(1 - beta)
      , breaks = function(x) seq(0.05, 0.95, 0.15)
      , labels = function(...) printp(..., digits = 2)
    ) +
    scale_color_viridis_c(
      name = bquote(rho)
      , end = 0.9
      , guide = guide_colorbar(title.position = "top", title.hjust = 0.5, direction = "vertical", barheight = unit(75, "pt"), barwidth = unit(12, "pt"), reverse = TRUE)
      , limits = c(-1, 1)
    ) +
    facet_grid(~ test, labeller = label_parsed) +
    guides(linetype = FALSE) +
    coord_flip(ylim = c(0.05, 1)) +
    papaja::theme_apa(box = TRUE) +
    theme(
      legend.position = c(0, 0.88)
      , legend.justification = c(0, 1)
      , legend.background = element_blank()
      , plot.title = element_text(margin = margin(b = rel(5)))
      , strip.text.x = element_text(margin = margin(b = rel(10)))
      , panel.grid.major.y = element_line(linetype = "22")
    )
```

@@

We analyzed standardized response latencies, that is, the time that elapsed between stimulus presentation and *correct* response divided by the standard deviation of all response latencies in a given block, Figure\ \@ref(fig:otm1-iat-plot).
To assess the reversal of the response mapping effect, we contrasted the common response mapping of Bob and negative words with the common mapping of Bob and positive words.
Hence, larger values represent more favorable indirect evaluations.

@@

```{r otm1-iat-plot, fig.cap = "(ref:otm1-iat-plot)"}
otm1_results_legend <- guide_legend(
    title = expression(atop("Valence order", atop(scriptstyle("Behavioral information"), scriptstyle("(Briefly flashed words)"))))
    , title.position = "top"
    , title.hjust = 0.5
    , reverse = TRUE
    , keyheight = 2
  )

@@

```{r explore-salience-asymmetry, eval = FALSE}
# Main effect of response mapping is significant for both image types
otm1_iat_lmerTest %>%
  emmeans(specs = ~ Congruent | imageType, at = list(imageType = c(-1, 1))) %>%
  pairs()
```

@@

```{r otm1-lmer-emm-2, cache = TRUE, results = "asis"}
otm1_iat_lmer_contrasts <- contrast(
  otm1_iat_lmer_emm
  , list(
    "Negative-positive" = c(1, -1, -1, 1, 0, 0, 0, 0)
    , "Positive-negative" = c(0, 0, 0, 0, 1, -1, -1, 1)
  )
) %>%
  apa_print
```

In line with the conventional ANOVA analysis, we found that response time differences suggested more favorable evaluations of Bob after the first than after the second block when the behavioral information was first positive and later negative, `r otm1_iat_lmer_contrasts$full_result$Positive_negative`.
Vice versa, response time differences suggested more favorable evaluations after the second than after the first block when descriptions of Bob were first negative and later positive, `r otm1_iat_lmer_contrasts$full_result$Negative_positive`.
Again, these results indicate that the self-reported evaluations and IAT scores were consistent.

@@

## Bayesian model comparison

@@

#### Direct and indirect evaluations

@@

```{r otm1-prior-sensitivity-replication, cache = TRUE, warning = FALSE}
manuscript_cache <- "manuscript_cache/latex/"

otm1_attitudes_collapsed <- knitr::load_cache(label = "otm1-bayesian-replication-restructure", object = "otm1_attitudes_collapsed", path = manuscript_cache)
otm1_n <- as.integer(nlevels(otm1_attitudes_collapsed$ParticipantNumber))

otm1_null_model_matrix <- knitr::load_cache(label = "otm1-bayesian-replication-design-matrix", object = "otm1_null_model_matrix", path = manuscript_cache)
otm1_unconstrained_model_matrix <- knitr::load_cache(label = "otm1-bayesian-replication-design-matrix", object = "otm1_unconstrained_model_matrix", path = manuscript_cache)

replication_rscales <- expand.grid(
  iat = seq(0.5, 1, length.out = 3)
  , rating = seq(sqrt(2)/2, 2, length.out = 3)
) %>% 
  filter(iat <= rating) %>%
  as.matrix %>% 
  `/`(., sqrt(2)) %>% # Rescale to ANOVA specification (see https://forum.cogsci.nl/discussion/3746/bayesfactor-scale-of-cauchy-prior-in-t-tests-and-anova)
  as.data.frame

@@

## Word recogniton and indirect evaluations

@@

```{r otm1-rydell-recognition-plot, fig.cap = "(ref:otm1-rydell-recognition-plot)", fig.width = 3.5, fig.height = 2.5}
otm1_mem %>%
  ggplot(aes(x = Location, y = Accuracy, shape = Location, fill = Location)) +
  geom_hline(yintercept = 0.5, color = grey(0.5)) +
  geom_violin(alpha = 0.3) +
  geom_sina(alpha = 0.5, size = 1) +
  stat_summary(fun.data = mean_cl_boot, color = "black", fun.args = list(B = 10000)) +
  scale_shape_manual(values = c(21, 23, 24)) +
  scale_color_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  scale_fill_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  labs(
    x = "Location"
    , y = "Recognition accuracy"
  ) +
  theme(legend.position = "none")
```

In contrast to the original results reported by @rydell_two_2006, the recognition accuracy of briefly flashed words was above chance  in this study, Figure\ \@ref(fig:otm1-rydell-recognition-plot).
Memory for these words may, thus, have interfered with the associative learning process and prevented the predicted reversal of the IAT score differences.
We, therefore, performed an exploratory regression analysis of the recognition accuracy of briefly flashed words and the IAT score difference between blocks used in the Bayesian analysis above.
Positive IAT score differences represent a more favorable evaluation after the block in which Bob was paired with positive behavioral information and briefly flashed negative words.
Conversely, negative IAT score differences between blocks indicate that the IAT effects reflect the valence of the briefly flashed words.
If word recognition indeed obstructed the associative learning process, we would expect to observe a positive relationship between the recognition accuracy and IAT score differences between blocks:
When the recognition for briefly flashed words is high, IAT score differences should reflect the valence of the behavioral information but not with the word valence.
We would expect to observe smaller and eventually negative IAT score differences as the recognition accuracy declines and associative learning takes over.
To account for measurement error in the recognition accuracy of briefy flashed words we fit an errors-in-variable regression model [@Klauer_Draine_Greenwald_1998].
Because the model assumes that predictor values are sampled from a Gaussian distribution truncated at 0, we probit-transformed the recognition accuracy.^[A standard linear regression analysis yielded the same results.]

(ref:prime-recognition-iat-difference) Scatterplot of the recognition accuracy of briefly flashed words (on probit scale) and evaluative differences in IAT scores between learning blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.
The regression line and confidence band represents predictions of the errors-in-variables model [@Klauer_Draine_Greenwald_1998].

@@

otm1_iat_delta %>%
  ggplot(aes(x = Accuracy, y = delta)) +
  geom_hline(yintercept = 0, linetype = "22") +
  geom_vline(xintercept = 0.5, linetype = "22") +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "eiv_lm", color = "black") +
  labs(
    x = bquote("Recognition accuracy ["~Phi^-1*(italic(p))~"]")
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  scale_x_continuous(trans = "probit") +
  theme_apa()
```

```{r prime-recognition-iat-difference-regression, results = "asis"}
otm1_iat_delta_eiv_lm_res <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = qnorm(Accuracy)) %>%
  eiv_lm(delta ~ Accuracy, data = ., n.optim = 10) %>% 
  apa_print
```

We did not detect a relationship between the recognition accuracy of briefly preseted words and IAT score differences between learning blocks, `r otm1_iat_delta_eiv_lm_res$full_result$Accuracy`.
Moreover, the positive intercept of the regression line indicates a positive IAT score difference despite at-chance word recognition accuracy, `r otm1_iat_delta_eiv_lm_res$full_result$Intercept`.
Hence, even for participants who exhibited no memory for briefly flashed words, IAT score differences reflected the valence of the behavioral information, see Figure\ \@ref(fig:prime-recognition-iat-difference).
These results provide no indication that the deviation of our findings from those reported by @rydell_two_2006 are attributable to the above-chance recognition of briefly flashed words in this study.

# Experiment 2

In the following we report the details of our a priori power analysis, provide details for the model specification used for the Bayesian model comparisons, and additional secondary analyses.

## Power analysis

As for Experiment 1, our power analyses focuses on this interaction and the theoretically relevant simple effects of *learning block*.
We estimate the sensitivity of our design using the R-package *Superpower* [@R-Superpower] for the contrast analyes using the R-package *emmeans* [@R-emmeans].
@rydell_two_2006 found the smallest learning block difference for IAT scores, $\hat\eta_p^2 = `r printp(rydell_pes)`$, $d_z \approx `r rydell_dz`$.
The learning block differences reported by @heycke_two_2018 were of similar magnitude but with an opposite sign.

```{r otm2-omnibus-power, cache = TRUE}
# Main effect block and three-way interaction
otm2_power <- function(f, n, rm_cor = 0.5, alpha = 0.05) {
  contrast_codes <- tibble::tibble(
    time = rep(contr.treatment(2), 4)
    , order = rep(rep(contr.sum(2), each = 2), 2)
    , block = rep(contr.sum(2), each = 4)
    , time_block = time * block
    , time_order = time * order
    , block_order = block * order
    , time_block_order = time * block * order
  )

  mu <- with(
    contrast_codes
    , -block_order * f +
      -block * 0.5 * f +
      time_block_order * f
  )

  string <- "2w*2b*2b"
  labelnames <- c("block", "1", "2", "order", "p-n", "n-p", "time", "13", "20")

  design_result <- ANOVA_design(
    design = string
    , n = n
    , mu = mu
    , sd = 1
    , r = rm_cor
    , labelnames = labelnames
  )

  ANOVA_exact(
    design_result
    , alpha_level = alpha_level
    , emm = FALSE
    , verbose = FALSE
  )
}

otm2_n <- 320/4

# 95% power
otm2_pes <- 0.03973071
otm2_dz <- pes_to_dz(otm2_pes, otm2_n, n_groups = 4)
rho <- 0.5
f <- dz_to_f(otm2_dz, rho)

# otm2_time_power <- otm2_power(f = f, n = otm2_n, rm_cor = rho, alpha = 0.05)
# otm2_time_power$main_result

otm2_dz_block <- f_to_dz(0.5*f, rho = rho)
otm2_pes_block <- dz_to_pes(otm2_dz_block, otm2_n, n_groups = 4)

otm2_dz_int <- f_to_dz(f, rho = rho)
otm2_pes_int <- dz_to_pes(otm2_dz_int, otm2_n, n_groups = 4)
```

```{r otm2-contrast-power, cache = TRUE}
otm2_power <- function(f, n, rm_cor = 0.5, alpha = 0.05) {
  contrast_codes <- tibble::tibble(
    time = rep(contr.treatment(2), 4)
    , order = rep(rep(contr.sum(2), each = 2), 2)
    , block = rep(contr.sum(2), each = 4)
    , time_block = time * block
    , time_order = time * order
    , block_order = block * order
    , time_block_order = time * block * order
  )

  mu <- with(
    contrast_codes
    , -order * 0.25*f +
      -block_order * f
  )

  string <- "2w*2b*2b"
  labelnames <- c("block", "1", "2", "order", "p-n", "n-p", "time", "13", "20")

  design_result <- ANOVA_design(
    design = string
    , n = n
    , mu = mu
    , sd = 1
    , r = rm_cor
    , labelnames = labelnames
  )
